Social Conditions of Fear

### 2023-11-22 scripts/manuscript.qmd
Replacing NA values with "NA" instead of different wordings as originally in the data

**Sociodemographics Variables** 1. "born": Were you born in this country? 2. "age" 3. "sexnow1": Do you describe yourself as male, female, or transgender? *This is self-described gender.* 4. "sex": Code respondent's sex *This is gender presentation as interpreted by the interviewer.* 4. "sexornt": Which of the following best describes you? 5. "racerank1": If you had to choose, which of these races do you identify most with? *Kept this race variable here instead of "race" because it allows more heterogeneity within group.* 6. "hispanic": Are you Spanish, Hispanic, or Latino/Latina? IF YES: Which group are you from? 7. "degree": Respondent's degree. 8. "uscitzn": Are you a US citizen? 9. "dwelown": (Do you/Does your family) own your (home/apartment), pay rent, or what?

@@

>>>>

**Sociodemographics Variables** 
1. "born": Were you born in this country? 
2. "age" 
3. "sexnow1": Do you describe yourself as male, female, or transgender? *This is self-described gender.* 
4. "sex": Code respondent's sex *This is gender presentation as interpreted by the interviewer.* 
5. "sexornt": Which of the following best describes you? 
6. "racerank1": If you had to choose, which of these races do you identify most with? *Kept this race variable here instead of "race" because it allows more heterogeneity within group.* 
7. "hispanic": Are you Spanish, Hispanic, or Latino/Latina? IF YES: Which group are you from? 
8. "degree": Respondent's degree. 
9. "uscitzn": Are you a US citizen? 
10. "dwelown": (Do you/Does your family) own your (home/apartment), pay rent, or what?

@@

view(na_data)
